\Large \bf 6.829 Final Project: A comparison of bit-rate selection algorithms

### 2013-05-16 paper/paper.tex
paper tweak
paper tweak2

Our examination of the histograms showed us that Minstrel spends a lot of time sampling at high rates. In the specific case we examined, they were all probe packets. But sometimes Minstrel would choose 54Mbps as the rate with the best throughput, which made little sense. A closer investigation revealed that Minstrel would sometimes luck out and get one success sending a probe at 54Mbps. The probability of success would be 1, so then 54Mbps would be chosen as the rate with the best throughput. This is unfortunate, but the real harm came in the next window: nearly all of the packets at 54Mbps would fail, but Minstrel was still considering 54 Mbps to be the best rate! This is because the EWMA did not account for the fact that the second block having sent hunreds more packets at 54 Mbps than the first. Thus the probability of success would drop from 1 to about 0.70, which is still high enough for the throughput equation to rank 54 Mbps highly. In essense, the probabilities were not declining fast enough after a large number of failures at some rate.

@@

Hari Balikrishnan suggested that we use a broadcast approach when collecting our traces, instead of link layer acknowledgements. This would entail having multiple computers listening at the broadcast address, and compiling successes and failures from that information. This approach would free us from certain idiosyncracies of reading data from the driver, and lead to possibly more accurate traces. We were unable to implement this due to a lack of time and ability to acquire compatible hardware.

@@

\section{Acknowledgements}
We would like to thank Jonathan Perry and Hari Balikrishnan for their valuable guidance, as well as Derek Smithies for answering our questions about Minstrel.

>>>>

Our examination of the histograms showed us that Minstrel spends a lot of time sampling at high rates. In the specific case we examined, they were all probe packets. But sometimes Minstrel would choose 54Mbps as the rate with the best throughput, which made little sense. A closer investigation revealed that Minstrel would sometimes luck out and get one success sending a probe at 54Mbps. The probability of success would be 1, so then 54Mbps would be chosen as the rate with the best throughput. This is unfortunate, but the real harm came in the next window: nearly all of the packets at 54Mbps would fail, but Minstrel was still considering 54 Mbps to be the best rate! This is because the EWMA did not account for the fact that the second block having sent hunreds more packets at 54 Mbps than the first. Thus the probability of success would drop from 1 to about 0.70, which is still high enough for the throughput equation to rank 54 Mbps highly. In essense, the probabilities were not declining fast enough after a large number of failures.

@@

Hari Balakrishnan suggested that we use a broadcast approach when collecting our traces, instead of link layer acknowledgements. This would entail having multiple computers listening at the broadcast address, and compiling successes and failures from that information. This approach would free us from certain idiosyncracies of reading data from the driver, and lead to possibly more accurate traces. We were unable to implement this due to a lack of time and ability to acquire compatible hardware.

@@

\section{Acknowledgements}
We would like to thank Jonathan Perry and Hari Balakrishnan for their valuable guidance, as well as Derek Smithies for answering our questions about Minstrel.
